---
title: "Results"
output: html_notebook
---

```{r Average networks results}
source("scripts/networks.R")

```

# Averaged networks

## Coefficients of each node (species)
Which predictors determine it's likelihood of occurrence

### Serranidae network
```{r}
S.cab.coeffs
S.scrib.coeffs

```

*Serranus cabrilla* and *Serranus scriba* are mostly affected by temperature.

```{r}
E.costae.coeffs
E.margin.coeffs

```

*Epinephelus marginatus* is mostly affected by *Epinephelus costae* but not the other way around.

```{r}
serr_effects
```

```{r}
serr_dists
```

### Diplodus network

```{r}
D.annu.coeffs
D.punt.coeffs
D.vulg.coeffs

```

*Diplodus annularis* is mostly affected by the interaction between temperature and the presence of *D. sargus*.

*Diplodus puntazzo* is mostly affected by the presence of *D. vulgaris*.

*Diplodus vulgaris* is strongly affected by temperature.

*Diplodus cervinus* is **only** affected by *D. sargus*.

### Herbivore network
```{r}
S.rev.coeffs
S.salpa.coeffs
S.ghob.coeffs
S.cret.coeffs
```

*Siganus rivulatus* is **only** affected by temperature, as is *Sarpa salpa*.
*Scarus ghobban* is affected by the interaction of temperature and the presence of *Siganus rivulatus*, as is *Sparisoma cretense*.

# Predicted networks

```{r Predicted networks results}
source("scripts/predict_nets.R")

```


Use bootstrapped model (`bootstrap_MRF`) for predicting log odds (logit) of occurrence for species per site (`predict_MRF`). These log odds can be transformed into probabilities using `LaplacesDemon::invlogit` function. These can be "checked" using subsets of the data by covariate levels (e.g. low/mid/hi temp) to create separate networks - not with the predict function but with the `MRFcov` function. ????

`bootstrap_MRF` creates distribution of data permutations and helps in eliminating uncertainties. Part of its output is 95% confidence interval for each one of the predictors, which I can use to evaluate the predictors effect.
























