---
title: "Results Quantification"
author: "Shira Salingre"
output: html_document
---

Quantifying networks for 

_Run `results_prelim.Rmd` to get all data sets and subsets_
```{r Source data from the results file, include=FALSE}
# source_rmd <- function(rmd_file){
#   knitr::knit(rmd_file, output = tempfile())
# }
# 
# source_rmd("results_prelim.Rmd")
source('scripts/quant_func.R')

```

# Groupers

## Relative importance of species only

```{r}
groupers_temp_relimp <- sapply(X = model_temp_grps$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "temp_model" = value)

groupers_mpa_relimp <- sapply(X = model_mpa_grps$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "mpa_model" = value)

groupers_depth_relimp <- sapply(X = model_depth_grps$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "depth_model" = value)

(groupers_spp_relimp <- groupers_temp_relimp %>%
  left_join(groupers_mpa_relimp, by = "species") %>% 
  left_join(groupers_depth_relimp, by = "species"))

```

## Sum of mean association coefficients for each species
```{r}
grps_temp_meancoefs <- sapply(X = model_temp_grps$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_temp" = value)

grps_mpa_meancoefs <- sapply(X = model_mpa_grps$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_mpa" = value)

grps_depth_meancoefs <- sapply(X = model_depth_grps$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_depth" = value)

(groupers_spp_meancoef <- grps_temp_meancoefs %>%
  left_join(grps_mpa_meancoefs, by = "species") %>% 
  left_join(grps_depth_meancoefs, by = "species"))

```


# Diplodus

## Relative importance of species only

```{r}
dip_temp <- sapply(X = model_temp_dip$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "temp_model" = value)

dip_mpa <- sapply(X = model_mpa_dip$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "mpa_model" = value)

dip_depth <- sapply(X = model_depth_dip$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "depth_model" = value)

(dip_spp_relimp <- dip_temp %>%
  left_join(dip_mpa, by = "species") %>% 
  left_join(dip_depth, by = "species"))

```

## Sum of mean association coefficients for each species
```{r}
dip_temp_meancoefs <- sapply(X = model_temp_dip$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_temp" = value)

dip_mpa_meancoefs <- sapply(X = model_mpa_dip$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_mpa" = value)

dip_depth_meancoefs <- sapply(X = model_depth_dip$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_depth" = value)

(dip_spp_meancoef <- dip_temp_meancoefs %>%
  left_join(dip_mpa_meancoefs, by = "species") %>% 
  left_join(dip_depth_meancoefs, by = "species"))

```

# Herbivores

## Relative importance of species only

```{r}
herb_temp <- sapply(X = model_temp_herb$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "temp_model" = value)

herb_mpa <- sapply(X = model_mpa_herb$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "mpa_model" = value)

herb_depth <- sapply(X = model_depth_herb$mod$key_coefs, rel_imp) %>% 
  tibble::enframe() %>% 
  rename("species" = name, "depth_model" = value)

(herb_spp_relimp <- herb_temp %>%
  left_join(herb_mpa, by = "species") %>% 
  left_join(herb_depth, by = "species"))

```

## Sum of mean association coefficients for each species
```{r}
herb_temp_meancoefs <- sapply(X = model_temp_herb$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_temp" = value)

herb_mpa_meancoefs <- sapply(X = model_mpa_herb$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_mpa" = value)

herb_depth_meancoefs <- sapply(X = model_depth_herb$boot$mean_key_coefs, FUN = mean_coef) %>%
  tibble::enframe() %>% 
  rename("species" = name, "sum_mean_coefs_depth" = value)

(herb_spp_meancoef <- herb_temp_meancoefs %>%
  left_join(herb_mpa_meancoefs, by = "species") %>% 
  left_join(herb_depth_meancoefs, by = "species"))

```

_Siganus rivulatus_ coefficients seem to be inflated in all variables (this is also why the)

