---
title: "Results"
author: "Shira Salingre"
output: 
  html_document:
    theme: united
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
# source("scripts/thesis_results_1.R")
source("R/run_models.R")
source("R/rel_imp.R")
source("R/effect_size.R")
```

## Compare association coefficients

Association coefficients describe the relationship between species. Looking at the mean species correlations (**associations**), we can see a stationary (static) or non-stationary (dynamic) pattern:

```{r}
# Groupers
gridExtra::grid.arrange(grpsHM_cov, grpsHM_nocov, nrow = 1, top = "Groupers co-occurrence")

# Seabreams
gridExtra::grid.arrange(dipHM_cov, dipHM_nocov, nrow = 1, top = "Seabream co-occurrence")

# Herbivores
gridExtra::grid.arrange(herbHM_cov, herbHM_nocov, nrow = 1, top = "Herbivores co-occurrence")
```

All species exhibit non-stationarity. When covariates are introduced (left graph in all three panels), species associations change. In the groupers taxa it is extremely evident as most associations are completely gone and the only one that's left (*Epinephelus marginatus* and *Epinephelus costae*) seem to be weaker. All negative associations that were found when no covariates were introduced, are minimised to zero.
The associations of seabreams are also highly affected by the introduction of covariates: all associations that exist when not accounting for covariates are minimised to zero, while others strengthen. The coefficients are also minimised.
The herbivorous species exhibit the most subtle variance: though most associations are minimised to zero when accounting for covariates, on species pair (*Scarus ghobban* and *Siganus luridus*) still show a strong negative association. This is a particulary interesting results because both are limited to the eastern basin of the Mediterranean, both are exotic species and the association here is negative (as oppose to other taxa).
Overall we can see clearly that biotic co-occurrence patterns change when accounting for environmental and anthropogenic covariates.


## Nonstationarity

How important is non-stationarity in fish networks in the Mediterranean?

### For all three taxa

```{r}
all_relimp %>% bind_rows(.id = "taxa") %>% pivot_longer(3:length(.)) %>% # Create a tibble of all taxa
  rename(taxa = taxa, species = species, covariate = name, rel_imp = value) %>%
  mutate(covariate = str_remove(string = covariate, pattern = "_rel_imp")) %>% 
  ggplot() +
  aes(x = covariate, y = rel_imp, fill = taxa)+
  stat_summary(geom = "bar", fun = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  scale_fill_manual(values = wesanderson::wes_palette(n = 3, name = "Darjeeling2")) +
  labs(title = "Relative importance of factors in the model", subtitle = "All three taxa mean")
```

The interaction between temperature/mpa and biotic factors (what points out non-stationarity) is relatively low, which indicates a rather small non-stationarity. Nevertheless, the variance over the mean is very high, so let's have a closer look into the means over the species in each taxa:
```{r}
all_relimp %>% bind_rows(.id = "taxa") %>% pivot_longer(3:length(.)) %>% # Create a tibble of all taxa
  rename(taxa = taxa, species = species, covariate = name, rel_imp = value) %>%
  mutate(covariate = str_remove(string = covariate, pattern = "_rel_imp")) %>% 
  ggplot() +
  aes(x = covariate, y = rel_imp, fill = taxa)+
  stat_summary(geom = "bar", fun = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  facet_wrap(~taxa, nrow = 1) +
  scale_fill_manual(values = wesanderson::wes_palette(n = 3, name = "Darjeeling2")) +
  labs(title = "Relative importance of factors in the model", subtitle = "Mean for each taxa") +
  theme(legend.position = "none")
```
Groupers exhibit stationarity.

# Effect size
```{r}
mean_effect_size %>% 
  pivot_longer(cols = 3:ncol(.), names_to = "covariate") %>% 
  ggplot() +
  aes(x = covariate, y = value, fill = taxa) +
  geom_abline(aes(intercept = 0, slope = 0), col = "red", linetype = "dashed") +
  geom_boxplot() +
  facet_wrap(~taxa, nrow = 1) +
  scale_fill_manual(values = wesanderson::wes_palette(n = 3, name = "Darjeeling2")) +
  theme(legend.position = "none")

```

There isn't a prominent effect size in the groupers taxa. Herbivores seem to be affected negatively by anthropogenic factors (MPAs) and seabreams are affected negatively by MPAs and positively by temperature*biotic.

## Networks

### Temperature
```{r}
grps_plot
dip_plot
herb_plot
```

### MPA
```{r}
grps_mpa_plot
dip_mpa_plot
herb_mpa_plot
```

<!-- ## Predictions  -->
<!-- Not sure how this works: what are the units of prediction? -->
<!-- **temperature**   -->
<!-- ```{r} -->
<!-- gridExtra::grid.arrange(ec_plot, em_plot, mr_plot, ss_plot, sc_plot, nrow = 2) -->
<!-- gridExtra::grid.arrange(da_plot, dp_plot, ds_plot, dv_plot, dc_plot, nrow = 2) -->
<!-- gridExtra::grid.arrange(sr_plot, sl_plot, sas_plot, sg_plot, spc_plot, nrow = 2) -->
<!-- ``` -->

<!-- **MPAs**   -->
<!-- ```{r} -->
<!-- gridExtra::grid.arrange(ec_boxplot, em_boxplot, mr_boxplot, ss_boxplot, sc_boxplot, nrow = 2) -->
<!-- gridExtra::grid.arrange(da_boxplot, dp_boxplot, ds_boxplot, dv_boxplot, dc_boxplot, nrow = 2) -->
<!-- gridExtra::grid.arrange(sr_boxplot, sl_boxplot, sas_boxplot, sg_boxplot, spc_boxplot, nrow = 2) -->
<!-- ``` -->




<!-- Connectance (Delams _et al._ [^2]) is a measure of comparison between networks. Essentially, it describes the level of connectedness of species in the network as a proportion the potential associations in the network: -->

<!--     C0 = [total # of edges] / [total # of nodes^2 (total possible connections)] -->

<!-- L = number of edges (associations)   -->
<!-- S = number of nodes (species)   -->
<!-- M = S^2   -->
<!-- connectance (C0) = L/M   -->

___

[^1]: Clark, Nicholas J., Konstans Wells, and Oscar Lindberg. "Unravelling changing interspecific interactions across environmental gradients using Markov random fields." Ecology 99.6 (2018): 1277-1283.

[^2]: Delmas, E., Besson, M., Brice, M. H., Burkle, L. A., Dalla Riva, G. V., Fortin, M. J., ... & Olesen, J. M. (2019). Analysing ecological networks of species interactions. Biological Reviews, 94(1), 16-36.

