---
title: "Results"
author: "Shira Salingre"
output: 
  html_document:
    theme: united
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
source("scripts/pckgs_preps.R")
source("scripts/thesis_results_1.R")

```

# Objectives  

1. To estimate the amount of non-stationarity in interspecific interactions within fish communities across the Mediterranean Sea.  
2. To estimate the amount of non-stationarity in interspecific interactions within fish communities within and outside MPAs.  

# Predictions:

1. Temperature effect:
  a. More **positive** associations  
  b. More **negative** associations
  * CREATE A GRAPH (X = TEMPERATURE; Y = SUM OF ASSOCIATIONS or COUNT OF POSITIVE/NEGATIVE ASSOCIATIONS)  
2. MPA effect:
  a. More species/individuals/biomass can be translated to more associations
  b. In biomass model - more associations
  
# Data

## Species  
In order to examine the association between species and how this association changes along environmental gradient, I chose three groups of representative fish species (taxa): groupers (Epinephelus species + Serranus species), seabream species and herbivorous species.  

## Covariates  

I included 6 covariates:

* Annual surface temperature (standardised)
* Mean depth (standardised)
* MPAs - unprotected (enforcement level 0-1) or protected (2-3)
* Primary productivity (standardised)
* Salinity (standardised)
* Country - to account for spatial autocorrelation (coordinates are rough, so I used country instead)

## Model  
I'm using the MRF-based model from `MRFcov` package (Clark _et al._ [^1]) to detemine the level and direction of species association in each group.  

<!-- From Roi's comments on proposal: 

- Is there any grounds to hypothesise that in warmer areas the associations will be going a certain direction? (more/less associations, weaker/stringer associations) --- NETWORK LEVEL  
- How to identify patterns?  
- Invasive species gradient --- WE CAN MAKE A SORT OF INDEX OF INVASION  
- What variable is being measured? Strength of associations? Direction of associations? Count of associations?  

**I THINK WE SHOULD USE DIFFERENT VARIABLES FOR DIFFERENT QUESTIONS**  


-->

# Analyses

## Compare association coefficients

Association coefficients describe the relationship between species. Looking at the mean species correlations (**associations**), we can see a stationary (static) or non-stationary (dynamic) pattern:

```{r}
# Groupers
gridExtra::grid.arrange(grpsHM_cov, grpsHM_nocov, nrow = 1, top = "Groupers co-occurrence")

# Seabreams
gridExtra::grid.arrange(dipHM_cov, dipHM_nocov, nrow = 1, top = "Seabream co-occurrence")

# Herbivores
gridExtra::grid.arrange(herbHM_cov, herbHM_nocov, nrow = 1, top = "Herbivores co-occurrence")
```

## Number of associations

```{r}
all_assoc
```

## Relative importance of covariates

### Per species
```{r}
all_relimp
```

```{r}
all_relimp %>% bind_rows(.id = "taxa") %>%
  pivot_longer(3:6) %>% # Create a tibble of all taxa
  rename(taxa = taxa, species = species, covariate = name, rel_imp = value) %>%
  mutate(covariate = str_remove(string = covariate, pattern = "_rel_imp")) %>% 
  ggplot() +
  aes(x = covariate, y = rel_imp, fill = taxa)+
  stat_summary(geom = "bar", fun = mean, position = "dodge")+
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")
```

There's a large variance between species in the taxa so maybe this isn't the right way to look at it.

<!-- Connectance (Delams _et al._ [^2]) is a measure of comparison between networks. Essentially, it describes the level of connectedness of species in the network as a proportion the potential associations in the network: -->

<!--     C0 = [total # of edges] / [total # of nodes^2 (total possible connections)] -->

<!-- L = number of edges (associations)   -->
<!-- S = number of nodes (species)   -->
<!-- M = S^2   -->
<!-- connectance (C0) = L/M   -->

___

[^1]: Clark, Nicholas J., Konstans Wells, and Oscar Lindberg. "Unravelling changing interspecific interactions across environmental gradients using Markov random fields." Ecology 99.6 (2018): 1277-1283.

[^2]: Delmas, E., Besson, M., Brice, M. H., Burkle, L. A., Dalla Riva, G. V., Fortin, M. J., ... & Olesen, J. M. (2019). Analysing ecological networks of species interactions. Biological Reviews, 94(1), 16-36.

