---
title: "Results"
author: "Shira Salingre"
output: 
  html_document:
    theme: united
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
source("scripts/thesis_results_1.R")

```

# Objectives  

1. To estimate the amount of non-stationarity in interspecific interactions within fish communities across the Mediterranean Sea.  
2. To estimate the amount of non-stationarity in interspecific interactions within fish communities within and outside MPAs.  

# Predictions:

1. Temperature effect:
  a. More **positive** associations  
  b. More **negative** associations
  * CREATE A GRAPH (X = TEMPERATURE; Y = SUM OF ASSOCIATIONS or COUNT OF POSITIVE/NEGATIVE ASSOCIATIONS)  
2. MPA effect:
  a. More species/individuals/biomass can be translated to more associations
  b. In biomass model - more associations
  
# Data

## Species  
In order to examine the association between species and how this association changes along environmental gradient, I chose three groups of representative fish species (taxa): groupers (Epinephelus species + Serranus species), seabream species and herbivorous species.  

## Covariates  

I included 6 covariates:

* Annual surface temperature (standardised)
* Mean depth (standardised)
* MPAs - unprotected (enforcement level 0-1) or protected (2-3)
* Primary productivity (standardised)
* Salinity (standardised)
* Country - to account for spatial autocorrelation (coordinates are rough, so I used country instead)

## Model  
I'm using the MRF-based model from `MRFcov` package (Clark _et al._ [^1]) to detemine the level and direction of species association in each group.  

<!-- From Roi's comments on proposal: 

- Is there any grounds to hypothesise that in warmer areas the associations will be going a certain direction? (more/less associations, weaker/stringer associations) --- NETWORK LEVEL  
- How to identify patterns?  
- Invasive species gradient --- WE CAN MAKE A SORT OF INDEX OF INVASION  
- What variable is being measured? Strength of associations? Direction of associations? Count of associations?  

**I THINK WE SHOULD USE DIFFERENT VARIABLES FOR DIFFERENT QUESTIONS**  


-->

# Analyses

## Compare association coefficients

Association coefficients describe the relationship between species. Looking at the mean species correlations (**associations**), we can see a stationary (static) or non-stationary (dynamic) pattern:

```{r}
# Groupers
gridExtra::grid.arrange(grpsHM_cov, grpsHM_nocov, nrow = 1, top = "Groupers co-occurrence")

# Seabreams
gridExtra::grid.arrange(dipHM_cov, dipHM_nocov, nrow = 1, top = "Seabream co-occurrence")

# Herbivores
gridExtra::grid.arrange(herbHM_cov, herbHM_nocov, nrow = 1, top = "Herbivores co-occurrence")
```

All species exhibit non-stationarity. When covariates are introduced (left graph in all three panels), species associations change. In the groupers taxa it is extremely evident as most associations are completely gone and the only one that's left (*Epinephelus marginatus* and *Epinephelus costae*) seem to be weaker. All negative associations that were found when no covariates were introduced, are minimised to zero.
The associations of seabreams are also highly affected by the introduction of covariates: all associations that exist when not accounting for covariates are minimised to zero, while others strengthen. The coefficients are also minimised.
The herbivorous species exhibit the most subtle variance: though most associations are minimised to zero when accounting for covariates, on species pair (*Scarus ghobban* and *Siganus luridus*) still show a strong negative association. This is a particulary interesting results because both are limited to the eastern basin of the Mediterranean, both are exotic species and the association here is negative (as oppose to other taxa).
Overall we can see clearly that biotic co-occurrence patterns change when accounting for environmental and anthropogenic covariates.

<!--See if I can do the same with models with and without anthropogenic-->

## Number of associations

```{r}
all_assoc
```

<!--Change to include only biotic associations-->

## Relative importance of covariates

### Per species
```{r}
all_relimp
```

**Groupers**  

- *Epinephelus costae* is mainly affected by biotic factors.
- *Serranus cabrilla* is affected almost exlusively by environmental factors.

**Seabreams**  

- *Diplodus vulgaris* is mostly affected by environmental variables.
- *Diplodus cervinus* is affected only by environmental variables.

**Herbivores**  
*Siganus rivulatus* and *Sarpa salpa* are highly effected by environmental variables. They may have a simialr response to environmental variations.

### Per taxa

```{r}
all_relimp %>% bind_rows(.id = "taxa") %>%
  pivot_longer(3:6) %>% # Create a tibble of all taxa
  rename(taxa = taxa, species = species, covariate = name, rel_imp = value) %>%
  mutate(covariate = str_remove(string = covariate, pattern = "_rel_imp")) %>% 
  ggplot() +
  aes(x = covariate, y = rel_imp, fill = taxa)+
  stat_summary(geom = "bar", fun = mean, position = "dodge")+
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")
```

There's a large variance between species in the taxa so maybe this isn't the right way to look at it.

<!-- Connectance (Delams _et al._ [^2]) is a measure of comparison between networks. Essentially, it describes the level of connectedness of species in the network as a proportion the potential associations in the network: -->

<!--     C0 = [total # of edges] / [total # of nodes^2 (total possible connections)] -->

<!-- L = number of edges (associations)   -->
<!-- S = number of nodes (species)   -->
<!-- M = S^2   -->
<!-- connectance (C0) = L/M   -->

___

[^1]: Clark, Nicholas J., Konstans Wells, and Oscar Lindberg. "Unravelling changing interspecific interactions across environmental gradients using Markov random fields." Ecology 99.6 (2018): 1277-1283.

[^2]: Delmas, E., Besson, M., Brice, M. H., Burkle, L. A., Dalla Riva, G. V., Fortin, M. J., ... & Olesen, J. M. (2019). Analysing ecological networks of species interactions. Biological Reviews, 94(1), 16-36.

