---
title: "Results"
output: html_notebook
---

**How fish communities change along environmental gradients?**

Species associations are represented graphically and quantitatively using *MRFcov package* [^1].

```{r Load packages, functions and data, message=FALSE, warning=FALSE, include=FALSE}

source("scripts/pckgs_preps.R")
source("scripts/model_func.R")

```


# Mediterranean networks

Networks for the whole Mediterranean sea, accounting for spatial autocorrelation.

## Groupers

### Temperature as covariate

```{r}
# Create species matrix for `group` in `basin` with `covariate`
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "tmean_reg")

# a) Extract species matrix
spp_mat <- spp_data[[1]]
nrow(spp_mat)

# b) Extract coordinate dataframe:
coords <- spp_data[[2]]
nrow(coords)

# Run model and create occurrence predictions
model_temp <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_temp <- model_temp$mod$direct_coefs
key_coef_temp <- model_temp$boot$mean_key_coefs
predict_temp <- model_temp$pred

# Categorise continuous data + Nest categorical (nominal) data
categories <- categorise_cov(species_mat = spp_mat, covariate = "tmean_reg")
nested_cats <- nested_data(categorised_data = categories)

# Run MRFcov model with some defaults
cat_model <- get_model(data = spp_mat, ncov = 1)
cat_model

# Run model on each category
nested <- nested_models(nested_df = nested_cats)

# Get graph data
nested_plot <- nested %>% mutate(plot = map(model, get_graph))

# Plot multiple graphs for gradient
temperature_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/groupers_allmed_temp.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```

### MPA as covariate
```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "mpa")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_enf <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_enf <- model_enf$mod$direct_coefs
key_coef_enf <- model_enf$boot$mean_key_coefs
predict_enf <- model_enf$pred

# Func 3b (no need for 3a because it's already categorised) - nesting only
nested_cats <- nested_data(categorised_data = as.data.frame(spp_mat))

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

MPAs_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 2) 

# png("figures/groupers_allmed_mpa.png", height = 450, width = 1600, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 2)
# dev.off()

```

### Depth as covariate

This one is problematic and might be excluded

```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "depth_reg")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_dep <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_dep <- model_dep$mod$direct_coefs
key_coef_dep <- model_dep$boot$mean_key_coefs
predict_dep <- model_dep$pred

categories <- categorise_cov(species_mat = spp_mat, covariate = "depth_reg")
nested_cats <- nested_data(categorised_data = categories)

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

depth_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/groupers_allmed_depth.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```



## Diplodus

### Temperature as covariate

```{r}
# Create species matrix for `group` in `basin` with `covariate`
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = diplodus, covariate = "tmean_reg")

# a) Extract species matrix
spp_mat <- spp_data[[1]]
nrow(spp_mat)

# b) Extract coordinate dataframe:
coords <- spp_data[[2]]
nrow(coords)

# Run model and create occurrence predictions
model_temp <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_temp <- model_temp$mod$direct_coefs
key_coef_temp <- model_temp$boot$mean_key_coefs
predict_temp <- model_temp$pred

# Categorise continuous data + Nest categorical (nominal) data
categories <- categorise_cov(species_mat = spp_mat, covariate = "tmean_reg")
nested_cats <- nested_data(categorised_data = categories)

# Run MRFcov model with some defaults
cat_model <- get_model(data = spp_mat, ncov = 1)
cat_model

# Run model on each category
nested <- nested_models(nested_df = nested_cats)

# Get graph data
nested_plot <- nested %>% mutate(plot = map(model, get_graph))

# Plot multiple graphs for gradient
temperature_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/diplodus_allmed_temp.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```

### MPA as covariate
```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = diplodus, covariate = "mpa")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_enf <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_enf <- model_enf$mod$direct_coefs
key_coef_enf <- model_enf$boot$mean_key_coefs
predict_enf <- model_enf$pred

# Func 3b (no need for 3a because it's already categorised) - nesting only
nested_cats <- nested_data(categorised_data = spp_mat)

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

MPAs_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 2) 

# png("figures/diplodus_allmed_mpa.png", height = 450, width = 1600, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 2)
# dev.off()

```

### Depth as covariate

This one is problematic and might be excluded

```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "depth_reg")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_dep <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_dep <- model_dep$mod$direct_coefs
key_coef_dep <- model_dep$boot$mean_key_coefs
predict_dep <- model_dep$pred

categories <- categorise_cov(species_mat = spp_mat, covariate = "depth_reg")
nested_cats <- nested_data(categorised_data = categories)

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

depth_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/groupers_allmed_depth.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```

Depths range is too small for analysis 2-11 metres. and the data isn't distributed well enough between them.
Check it with:

```{r eval=FALSE, include=FALSE}
spp_mat$depth %>% table

```

# Herbivores

### Temperature as covariate

```{r}
# Create species matrix for `group` in `basin` with `covariate`
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "tmean_reg")

# a) Extract species matrix
spp_mat <- spp_data[[1]]
nrow(spp_mat)

# b) Extract coordinate dataframe:
coords <- spp_data[[2]]
nrow(coords)

# Run model and create occurrence predictions
model_temp <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_temp <- model_temp$mod$direct_coefs
key_coef_temp <- model_temp$boot$mean_key_coefs
predict_temp <- model_temp$pred

# Categorise continuous data + Nest categorical (nominal) data
categories <- categorise_cov(species_mat = spp_mat, covariate = "tmean_reg")
nested_cats <- nested_data(categorised_data = categories)

# Run MRFcov model with some defaults
cat_model <- get_model(data = spp_mat, ncov = 1)
cat_model

# Run model on each category
nested <- nested_models(nested_df = nested_cats)

# Get graph data
nested_plot <- nested %>% mutate(plot = map(model, get_graph))

# Plot multiple graphs for gradient
temperature_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/groupers_allmed_temp.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```

### MPA as covariate
```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "mpa")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_enf <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_enf <- model_enf$mod$direct_coefs
key_coef_enf <- model_enf$boot$mean_key_coefs
predict_enf <- model_enf$pred

# Func 3b (no need for 3a because it's already categorised) - nesting only
nested_cats <- nested_data(categorised_data = spp_mat)

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

MPAs_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 2) 

# png("figures/groupers_allmed_mpa.png", height = 450, width = 1600, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 2)
# dev.off()

```

### Depth as covariate

```{r}
spp_data <- create_spp_mat(dataset = med_raw, basin = all_med,
                                group = groupers, covariate = "depth_reg")

spp_mat <- spp_data[[1]]
coords <- spp_data[[2]]
nrow(spp_mat) == nrow(coords)

model_dep <- run_mod(species_mat = spp_mat, n_covs = 1, family = "gaussian", coords = coords)
coef_dep <- model_dep$mod$direct_coefs
key_coef_dep <- model_dep$boot$mean_key_coefs
predict_dep <- model_dep$pred

categories <- categorise_cov(species_mat = spp_mat, covariate = "depth_reg")
nested_cats <- nested_data(categorised_data = categories)

cat_model <- get_model(data = spp_mat, ncov = 1)

nested <- nested_models(nested_df = nested_cats)

nested_plot <- nested %>% mutate(plot = map(model, get_graph))

depth_graph <- plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)

# png("figures/groupers_allmed_depth.png", height = 450, width = 1200, res = 150)
# plot_multi_graphs(nested_df = nested_plot, n_graphs = 3)
# dev.off()

```

Again, a problem with the data distribution of depth data


# Data visualisations

## Covariates

### Temperature distribution
```{r}
ggplot(med_raw, aes(tmean)) + geom_histogram(binwidth = 0.5, aes(fill = ..x..)) +
  labs(x = "Mean annual temperature", y = "Frequency", title = "Temperature") +
  guides(fill = FALSE)


```

### Depth distribution
```{r}
ggplot(med_raw, aes(depth)) + geom_histogram(binwidth = 1, aes(fill = ..x..)) +
  labs(x = "Depth of transect", y = "Frequency", title = "Depth") +
  guides(fill = FALSE)

```

### MPAs (enforcement) distribution
```{r}
ggplot(med_raw, aes(enforcement)) + geom_histogram(binwidth = 1, aes(fill = ..x..)) +
  labs(x = "Level of enforcement", subtitle = "0 = No enforcement; 3 = Fully protected",
       y = "Frequency", title = "Depth") +
  guides(fill = FALSE)

```


___

[^1]: Clark, Nicholas J., Konstans Wells, and Oscar Lindberg. "Unravelling changing interspecific interactions across environmental gradients using Markov random fields." Ecology 99.6 (2018): 1277-1283.